Value Ordering, Discrepancies, and Restarts in Subgraph Solvers: \\ Some Half-Baked Mucking Around

### 2017-09-26 paper/paper.tex
Zoom, LAD, etc

?? Establish a baseline. Compare to older Glasgow2, Glasgow3, LAD, PathLAD, SND if we can get it to
run on the larger set of instances, VF2, maybe SAT just to have something to cite showing how bad
SAT is at this. Just use tailored in this plot. Possibly just use the 5,725 instances here to avoid
pain with lousy solvers.

>>>>

?? In \cref{figure:others} we show that our solver is the bestest.

\begin{figure}[tb]
    \centering
    \includegraphics*{gen-graph-others.pdf}

    \centering
    \includegraphics*{gen-graph-others-zoom.pdf}

    \caption{Cumulative number of instances solved over time, comparing our algorithm to other
    solvers. Below, zoomed in a bit ?? make this pretty.}
    \label{figure:others}
\end{figure}

?? Stick in Glasgow2, Glasgow3, VF2, SND if we can get it to run on the larger set of instances,
maybe SAT just to have something to cite showing how bad SAT is at this.
